---
title: "College Major analysis"
author: "Lumi"
date: "01/02/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The aim of this assignment is to study how income varies across college major categories. Specifically to answer the question: “Is there an association between college major category and income?”



Documentation of assignment

Read the data table and store them in a variable:

```{r}
college_data <- read.csv("https://query.data.world/s/uieteyrze67twkiujwxffsokaml44y", header=TRUE, stringsAsFactors=FALSE);
```

First we view the data with:

```{r}
head(college_data)
summary(college_data)
```
## Analysis

The first columns contains major codes and this will be ignored, while the second columns is the name of majors. I will use the major category in order to determine my regression analysis. First let us determine the distribution of graduate income

```{r}
as.numeric(college_data$Median)
```
```{r}
hist(college_data$Median,xlab="Median Income($)")
```

Set the median to a numeric variable and majot category to a factor

```{r}
Income_median<-as.numeric(college_data$Median)
major_category<-as.factor(college_data$Major_category)
```
and do the analysis

```{r}
fit_regr<- lm(Income_median~major_category)
summary(fit_regr)
```
## Conlcusion

There seems to be a significant relationship between the college major and graduate income with a R squared of 0.5717. Though the multivariate analysis (including other variables) might yield a different result.
